LAGOS lake depth

### 2020-04-14 figures/01_geometry.Rmd
show r2 on scatter

cowplot::plot_grid(
  cowplot::plot_grid(
  cowplot::plot_grid(gg_scatter_shape + 
                       labs(color = "") +
                       # theme(axis.title.x = element_blank()) +
                       theme_opts,
                     gg_scatter_reservoir + 
                       labs(color = "") +
                       theme(#axis.title.x = element_blank(), 
                             axis.title.y = element_blank()) +
                       theme_opts, 
                     ncol = 2),
  cowplot::plot_grid(ggplot() + geom_blank() + 
                       theme_opts + theme(axis.line = element_blank()), 
                     gg_slope_shape +
                       theme_opts,
                     gg_slope_reservoir + 
                       theme(axis.title.y = element_blank()) +
                       theme_opts,
                     ncol = 3, rel_widths = c(0.08, 1, 1)), 
                     rel_widths = c(1, 1), nrow = 2), 
 legend_panel, rel_heights = c(1, 0.12), ncol = 1
)
```

>>>>

cowplot::plot_grid(
  cowplot::plot_grid(
  cowplot::plot_grid(gg_scatter_shape + 
                       labs(color = "") +
                       # theme(axis.title.x = element_blank()) +
                       annotate("text", x = 2000, y = 300, label = "R^2 == 0.80",
                                parse = TRUE) +
                       theme_opts,
                     gg_scatter_reservoir + 
                       labs(color = "") +
                       # annotate("text", x = 1800, y = 500, label = "R^2 == 0.80",
                       #          parse = TRUE) +
                       theme(#axis.title.x = element_blank(), 
                             axis.title.y = element_blank()) +
                       theme_opts, 
                     ncol = 2),
  cowplot::plot_grid(ggplot() + geom_blank() + 
                       theme_opts + theme(axis.line = element_blank()), 
                     gg_slope_shape +
                       annotate("text", x = 0.33, y = 0.03, label = "R^2 == 0.17",
                                parse = TRUE) +
                       theme_opts,
                     gg_slope_reservoir + 
                         # annotate("text", x = 0.3, y = 0.03, label = "R^2 == 0.17",
                         #        parse = TRUE) +
                       theme(axis.title.y = element_blank()) +
                       theme_opts,
                     ncol = 3, rel_widths = c(0.08, 1, 1)), 
                     rel_widths = c(1, 1), nrow = 2), 
 legend_panel, rel_heights = c(1, 0.12), ncol = 1
)
```
